Argennon: A Scalable Smart Contract Platform

### 2021-07-14 tex/sections/argon.tex
Add the virtual signature concept
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argon programming language is a class-based, object-oriented language designed for writing Argennon's smart
contracts. The Argon programming language is inspired by Solidity and is similar to Java, with a number of aspects
of them omitted and a few ideas from other languages included. Argon is designed to be fully compatible with
the Argennon Virtual Machine and be able to use all advanced features of the Argennon blockchain.

Argon applications (i.e.\ smart contracts) are organized as sets of packages. Each package has its own set of names
for types, which helps to prevent name conflicts. Every package can contain an arbitrary number of classes.
Every Argon application is required
to have exactly one \texttt{main} method and one \texttt{initialize} method. The \texttt{main} method is the
only method of an Argon application which can be called by other smart contracts.

@@

Access level modifiers determine whether other classes can use a particular field or invoke a particular method or
if a method can be invoked externally by other smart contracts.

>>>>

The Argon programming language is a class-based, object-oriented language designed for writing Argennon smart
contracts. The Argon programming language is inspired by Solidity and is similar to Java, with a number of aspects
of them omitted and a few ideas from other languages included. Argon is designed to be fully compatible with
the Argennon Virtual Machine and be able to use all advanced features of the Argennon blockchain.

Argon applications (i.e.\ smart contracts) are organized as sets of packages. Each package has its own set of names
for types, which helps to prevent name conflicts. Every package can contain an arbitrary number of classes.
Every Argon application is required
to have exactly one \texttt{main} method and one \texttt{initialize} method. The \texttt{main} method is the
only method of an Argon application which would be called by other smart contracts.

@@

Access level modifiers determine whether other classes can use a particular field or invoke a particular method.

### 2021-07-14 tex/sections/avm.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon\footnote{the classical pronunciation should be used:\textipa{/Ar"gen.non/}} Virtual Machine (AVM) is an
abstract computing machine for executing Argennon's smart contracts. The
Argennon Virtual Machine knows nothing of the Argennon blockchain, transactions or any concept of gas usage, only of
Argennon's identifier tries and the concept of execution sessions.

Execution sessions are separate sessions of executing smart contract's code by the Argennon Virtual Machine.
Every execution session starts with a single method invocation, but does not necessarily end when
that method invocation completes. During an execution session additional method invocations could be scheduled,
which will be executed after the initial method completion.

An execution session may complete normally or abruptly. When an execution session completes abruptly, it will
not have any effects on the AVM state.

@@

All these identifiers are \emph{prefix codes}, and hence can be represented by
\emph{prefix trees}\footnote{Also called tries.}. The Argennon has three primitive prefix trees:
\emph{applications, accounts} and \emph{local}. Any identifier in Argennon is a
prefix code built by using one or more of these prefix trees:
\begin{itemize}
    \item \texttt{applicationID} is a prefix code built by \emph{applications} prefix tree.
    \item \texttt{accountID} is a prefix code built by \emph{accounts} prefix tree.
    \item \texttt{methodID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    a prefix code made by \emph{local} prefix tree: (\texttt{|} is the concatenating operator)

    \texttt{methodID = (applicationID|<local-prefix-code>)}
    \item \texttt{chunkID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    an \texttt{accountID} to a prefix code made by \emph{local} prefix tree:

    \texttt{chunkID = (applicationID|accountID|<local-prefix-code>)}
\end{itemize}

@@

Every AVM execution session has a queue of call stacks. A call stack contains all the information that is needed for
restoring the AVM state, and continuing the execution after the method invocation completes.
This information is represented by a \texttt{CallInfo} struct:
\begin{verbatim}
CallInfo {
    methodID,
    pc,
    localFrame,
    operandStack
}.
\end{verbatim}

@@

The Argennon Virtual Machine defines various run-time data areas that are used during an execution session
(i.e.\ transaction), Some of these data areas are persistent and are stored on the blockchain, Other data areas
are per execution session or per method invocation. These data areas are created when their context starts and
destroyed when their context ends.

@@

\note{The Argennon Virtual Machine does not have internal or external methods. All methods are considered internal
except the \texttt{dispatcher} method, which is the only external method of any smart contract.
This design enables the AVM to execute smart contracts with \emph{RESTful} APIs more efficiently.}

@@

A smart contract can read any chunk stored in the heap by having its \texttt{chunkID}. However, it can only modify
those chunks that was created by itself. In other words, every memory chunk in the AVM heap has an owner. Only
the owner can modify a chunk while anyone can read that chunk. The owner of a chunk can be easily determined
by the \texttt{applicationID} part of the chunk identifier.

@@

The Argennon Virtual Machine has four types of method invocation instruction:
\begin{itemize}
    \item \texttt{invoke\_internal}: invokes a method without changing the context of method execution. In other
    words, the invoked method can only modify the state of the current smart contract.
    A smart contract can invoke any method by \texttt{invoke\_internal} instruction, even if that method is an
    internal method of another smart contract. Since the invoked method will always be executed in the context of
    the invoking smart contract, a smart contract will not be able to modify another smart contract state by
    this instruction. This instruction facilitates code reuse and the usage of libraries.
    If the invoked method completes abruptly, that will cause the invoker method to complete abruptly too.
    \item \texttt{invoke\_dispatcher}: invokes the \texttt{dispatcher} method of a smart contract and changes the
    context of method execution to that
    smart contract. If the invoked method completes abruptly, that will cause the invoker method to complete
    abruptly too.
    \item \texttt{i\_invoke\_dispatcher, i\_invoke\_internal}: independently invokes a method. These instructions
    are similar to their \texttt{invoke} counterparts, with the difference that when
    the invoked method completes abruptly, the invoker method can continue execution. When a method invoked by
    an \texttt{i\_invoke} instruction completes abruptly, all changes made
    by the invoked method to the AVM state will be reverted and the instruction will act like
    a jump to the specified error handling code.
    \item \texttt{invoke\_native}: invokes a method that is not hosted by the Argennon Virtual Machine. By this
    instruction, high performance native methods of the hosting machine, such as GPU accelerated operations,
    could become available to AVM smart contracts. This instruction will not modify the AVM state.
    \item \texttt{invoke\_later}: invokes the \texttt{dispatcher} method of another smart contract by creating a new
    call stack. The created call stack is added at the end of the call stack queue, and
    the context of method execution will change after the execution of that call stack starts. This instruction does
    not modify the \texttt{pc} register and the execution of the
    invoker will continue after this instruction. As a result, \texttt{invoke\_later} can not return
    any values to the caller and the return value of the called method (if any) will be discarded. If the invoked
    method completes abruptly, it will cause \textbf{all the call stack queue to
    complete abruptly.}
\end{itemize}

@@

Each time a method is invoked a new local frame
and operand stack is created. If the method was invoked by an \texttt{i\_invoke} instruction,
the \texttt{Save()} function of the AVM heap is called before the execution of the method starts.

@@

\note{The AVM does not natively support polymorphism and virtual methods. A compiler could easily
generates appropriate code for implementing these features.}

@@

\note{Any AVM instruction may throw an exception. This happens when the execution cost of a transaction has exceeded
the declared execution cost of the transaction.}

@@

When a method completes abruptly, the call stack is used to restore the \texttt{pc} register of the invoker. If the pc
register points to an \texttt{invoke} instruction, the current method completes abruptly as well. Otherwise, if
the \texttt{pc} register is pointing to an \texttt{i\_invoke} instruction, the \texttt{Heap.Restore()} function is
called to restore the state of the AVM heap. Then, the
local frame and operand stack of the invoker is restored, and execution continues after branching to the error handling
code specified by the instruction operand.

When an invocation which was made by an \texttt{invoke\_later} instruction completes abruptly, the
heap snapshot that was saved before the start of the
execution of the first call stack is restored. This means
that all changes made by the execution session to the AVM heap will be completely reverted.

@@

The Argennon Virtual Machine provides low level reentrancy protection by defining a dedicated
instruction: \texttt{enter}. When a smart contract executes the \texttt{enter} instruction, it
can not execute that instruction again as long
as the method executing that instruction completes (abruptly or normally). If a smart contract tries to execute
the \texttt{enter} instruction, while the method executing that instruction for the first time has not yet completed,
an exception will be thrown.

Smart contracts can completely prevent reentrancy by executing \texttt{enter} instruction as the first instruction
of their \texttt{dispatcher} method.

@@

\begin{itemize}
    \item \texttt{alloc}: creates a new memory chunk of the specified size in the heap. the identifier
    of the new chunk will be the concatenation of the \texttt{applicationID} of the creator of the chunk and
    the \texttt{id} operand of the instruction. The \texttt{id} operand must be the concatenation of
    an \texttt{accountID} and a prefix code
    generated by the \emph{local} prefix tree: \texttt{id = accountID|localID}. If the identifier is not valid or
    if it already exists in the heap a catchable exception will be thrown.

    \item \texttt{delete}: deletes the chunk that its identifier is the concatenation of the current smart
    contract \texttt{applicationID} and the specified \texttt{id} operand. If the identifier is not valid or
    if the chunk was not found a catchable exception will be thrown.
\end{itemize}

When a smart contract allocates a new memory chunk, the identifier of the new chunk is not generated by
the AVM, instead the smart contract can choose an identifier itself. This is a very important feature of
the AVM heap, which allows smart contracts to use the AVM heap as a dictionary (map) data structure.
Since the \texttt{chunkID} is a prefix code, any smart contract has its own identifier space and a smart contract
can easily generate unique identifiers for its chunks.

The AVM requires the chosen identifier to be a prefix code made by concatenating a code compatible with
the \emph{accounts} prefix tree to a code compatible with the \emph{local} prefix tree. This requirement
enables AVM to detect invalid identifiers, while smart contracts can easily associate data with account identifiers.
At the same time, A smart contract is able to create maps with costume keys by appending local identifiers
to the zero \texttt{accountID}. Zero \texttt{accountID} does not correspond to a valid account in the Argennon
blockchain.

@@

In blockchain applications, we usually need to authorize certain operations. For example, for sending an asset
from a user to another user, first we need to make sure that the sender has authorized this operation. The
Argennon virtual machine has no built-in mechanism for authorizing operations, but it provides a rich set of
cryptographic instructions for validating signatures and cryptographic entities. By using these instructions and
passing cryptographic signatures as parameters to methods, a programmer, having user's public keys, can implement
the required logic for authorizing any operation.

@@

In Argennon, the root smart contract is an updatable smart contract, which can be updated by the Argennon consensus
protocol. This means that bugs or security vulnerabilities in the AVM standard library could be quickly patched and
smart contracts could benefit from bugfixes and improvements of the AVM standard library even if they are
non-updatable. Many important and useful functionalities,
such as fungible and non-fungible assets, access control mechanisms,
and general purpose DAOs are implemented in the Argennon standard library.

>>>>

The Argennon\footnote{the classical pronunciation should be used:\textipa{/Ar"gen.non/}} Virtual Machine (AVM) is an
abstract computing machine for executing Argennon smart contracts. The
Argennon Virtual Machine knows nothing of the Argennon blockchain, transactions or any concept of gas usage, only of
Argennon identifier tries and the concept of execution sessions.

Execution sessions are separate sessions of executing smart contract's code by the Argennon Virtual Machine.
Every execution session starts with a single method invocation, but does not necessarily end with
that method invocation. During an execution session additional method invocations could be scheduled,
which will be executed after the initial method completes.

An execution session may complete normally or abruptly. When an execution session completes abruptly, it will
not have any effects on the AVM's state.

@@

All these identifiers are \emph{prefix codes}, and hence can be represented by
\emph{prefix trees}\footnote{Also called tries.}. The Argennon has three primitive prefix trees:
\emph{applications, accounts} and \emph{local}. Any identifier in Argennon is a
prefix code built by using one or more of these prefix trees:
\begin{itemize}
    \item \texttt{applicationID} is a prefix code built by \emph{applications} prefix tree.
    \item \texttt{accountID} is a prefix code built by \emph{accounts} prefix tree. An \texttt{accountID} can
    not be \texttt{0x0} or \texttt{0x1}.
    \item \texttt{methodID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    a prefix code made by \emph{local} prefix tree: (\texttt{|} is the concatenating operator)
    \subitem \texttt{methodID = (applicationID|<local-prefix-code>)} .
    \item \texttt{chunkID} is a composite prefix code built by concatenating an \texttt{applicationID} to
    an \texttt{accountID} to a prefix code made by \emph{local} prefix tree:
    \subitem \texttt{chunkID = (applicationID|accountID)} or
    \subitem \texttt{chunkID = (applicationID|0x0|<local-prefix-code>)} or
    \subitem \texttt{chunkID = (applicationID|0x1|accountID|<local-prefix-code>)} .
\end{itemize}

@@

Every AVM execution session has a queue of call stacks. A call stack contains all the information that is needed for
restoring the AVM's state and continuing the execution after the method invocation completes.
This information is represented by a \texttt{CallInfo} struct:
\begin{verbatim}
CallInfo {
    methodID,
    pc,
    localFrame,
    operandStack
} .
\end{verbatim}

@@

The Argennon Virtual Machine defines various run-time data areas that are used during an execution session,
Some of these data areas are persistent and are stored on the blockchain, Other data areas
are per execution session or per method invocation. These data areas are created when their context starts and
destroyed when their context ends.

@@

\note{The Argennon Virtual Machine does not have internal or external methods. All methods are considered internal
except the \texttt{dispatcher} method, which is the only external method of any smart contract.
This design enables the AVM to execute \emph{RESTful} smart contracts more efficiently.}

@@

A smart contract can read any chunk stored in the heap by having its \texttt{chunkID}. However, it can only modify
those chunks that was created by itself. In other words, every memory chunk in the AVM's heap has an owner. Only
the owner can modify a chunk while anyone can read that chunk. The owner of a chunk can be easily determined
by the \texttt{applicationID} part of the chunk identifier.

@@

The Argennon Virtual Machine has four types of method invocation instruction:
\begin{itemize}
    \item \texttt{invoke\_internal}: invokes a method without changing the context of method execution. In other
    words, the invoked method can only modify the state of the current smart contract.
    A smart contract can invoke any method by \texttt{invoke\_internal} instruction, even if that method is an
    internal method of another smart contract. Since the invoked method will always be executed in the context of
    the invoking smart contract, a smart contract will not be able to modify another smart contract's state by
    this instruction. This instruction facilitates code reuse and the usage of libraries.
    If the invoked method completes abruptly, the invoker method completes abruptly too.
    \item \texttt{invoke\_dispatcher}: invokes the \texttt{dispatcher} method of a smart contract and changes the
    context of method execution to that
    smart contract. If the invoked method completes abruptly, that will cause the invoker method to complete
    abruptly too.
    \item \texttt{i\_invoke\_dispatcher, i\_invoke\_internal}: independently invokes a method. These instructions
    are similar to their \texttt{invoke} counterparts, with the difference that when
    the invoked method completes abruptly, the invoker method can continue execution. When a method invoked by
    an \texttt{i\_invoke} instruction completes abruptly, all changes made
    by the invoked method to the AVM's state will be reverted and the instruction will act like
    a jump to the specified error handling code.
    \item \texttt{invoke\_native}: invokes a method that is not hosted by the Argennon Virtual Machine. By this
    instruction, high performance native methods of the hosting machine, such as GPU accelerated operations,
    could become available to AVM smart contracts. This instruction will not modify the AVM's state.
    \item \texttt{invoke\_later}: invokes the \texttt{dispatcher} method of another smart contract by creating a new
    call stack. The created call stack is added at the end of the call stack queue, and
    the context of method execution will change after the execution of that call stack starts. This instruction does
    not modify the \texttt{pc} register and the execution of the
    invoker will continue after this instruction. As a result, \texttt{invoke\_later} can not return
    any values to the caller and the return value of the called method (if any) will be discarded. If the invoked
    method completes abruptly, it will cause \textbf{all the call stack queue to
    complete abruptly.}
\end{itemize}

@@

Each time a method is invoked a new local frame
and operand stack is created. If the method was invoked by an \texttt{i\_invoke} instruction,
the \texttt{Save()} function of the AVM's heap is called before the execution of the method starts.

@@

\note{The AVM does not natively support polymorphism and virtual methods. A compiler could easily
generate appropriate code for implementing these features.}

@@

\note{Any AVM instruction may throw an exception. This happens when the execution cost of a transaction has exceeded
the declared maximum execution cost.}

@@

When a method completes abruptly, the call stack is used to restore the \texttt{pc} register of the invoker. If the pc
register points to an \texttt{invoke} instruction, the current method completes abruptly as well. Otherwise, if
the \texttt{pc} register is pointing to an \texttt{i\_invoke} instruction, the \texttt{Heap.Restore()} function is
called to restore the state of the AVM's heap. Then, the
local frame and operand stack of the invoker is restored, and execution continues after branching to the error handling
code specified by the instruction's operand.

When an invocation which was made by an \texttt{invoke\_later} instruction completes abruptly, the
heap snapshot that was saved before the start of the
execution of the first call stack is restored. This means
that all changes made by the execution session to the AVM's heap will be completely reverted.

@@

The Argennon Virtual Machine provides low level reentrancy protection by defining a dedicated
instruction: \texttt{enter}. When a smart contract executes the \texttt{enter} instruction, it
can not execute that instruction again as long
as the method executing the instruction completes (abruptly or normally). If a smart contract tries to execute
the \texttt{enter} instruction while the method executing that instruction for the first time has not yet completed,
an exception will be thrown.

Smart contracts can completely prevent reentrancy by executing the \texttt{enter} instruction as the first instruction
of their \texttt{dispatcher} method.

@@

\begin{itemize}
    \item \texttt{alloc}: creates a new memory chunk of the specified size in the heap. The
    new chunk's identifier will be the concatenation of the \texttt{applicationID} of the creator of the chunk and
    the \texttt{id} operand of the instruction. The \texttt{id} operand must be the concatenation of
    an \texttt{accountID} and a prefix code
    generated by the \emph{local} prefix tree: \texttt{id = accountID|localID}. If the identifier is not valid or
    if it already exists in the heap, a catchable exception will be thrown.

    \item \texttt{delete}: deletes the chunk that its identifier is the concatenation of the current smart
    contract \texttt{applicationID} and the specified \texttt{id} operand. If the identifier is not valid or
    if the chunk was not found, a catchable exception will be thrown.
\end{itemize}

When a smart contract allocates a new memory chunk, the identifier of the new chunk is not generated by
the AVM. Instead, the smart contract can choose an identifier itself. This is a very important feature of
the AVM's heap, which allows smart contracts to use the AVM's heap as a dictionary (map) data structure.
Since the \texttt{chunkID} is a prefix code, any smart contract has its own identifier space, and a smart contract
can easily generate unique identifiers for its chunks.

The AVM requires the chosen identifier to be a prefix code compatible with
the \emph{accounts} prefix tree, or a code made by concatenating a code compatible with
the \emph{accounts} prefix tree to a code compatible with the \emph{local} prefix tree. This requirement
enables AVM to detect invalid identifiers, while smart contracts can easily associate data with account identifiers.
At the same time, A smart contract is able to create maps with costume keys by appending local identifiers
to the zero \texttt{accountID}. Zero \texttt{accountID} does not correspond to a valid account in the Argennon
blockchain.

@@

In blockchain applications, we usually need to authorize certain operations. For example, for sending an asset
from a user to another user, first we need to make sure that the sender has authorized this operation. The
Argennon Virtual Machine has no built-in mechanism for authorizing operations, but it provides a rich set of
cryptographic instructions for validating signatures and cryptographic entities. By using these instructions and
passing cryptographic signatures as parameters to methods, a programmer, having users' public keys, can implement
the required logic for authorizing any operation.

@@

In Argennon, the root smart contract is an updatable smart contract, which can be updated by the Argennon governance
system. This means that bugs or security vulnerabilities in the AVM standard library could be quickly patched and
smart contracts could benefit from bugfixes and improvements of the AVM standard library even if they are
non-updatable. Many important and useful functionalities,
such as fungible and non-fungible assets, access control mechanisms,
and general purpose DAOs are implemented in the Argennon standard library.

### 2021-07-14 tex/sections/elements.tex
Fix some typos
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

Argennon has two special smart contracts: the \emph{root smart contract}, also called the \emph{root application}, and
the \emph{ARG smart contract}, which is also called the Argennon smart contract or the \emph{ARG application}.

@@

The root application or the root smart contract, with \texttt{applicationID = 0}, is a privileged smart contract
responsible for installation/uninstallation of other smart contracts. The Argennon root smart contract
performs three main operations:

@@

As a result, every Argennon transaction contains two HTTP requests. In addition to these HTTP requests, the
transaction is required to contain a resource declaration object, specifying the maximum amount of resources
it needs for execution.

@@

As we know, every Argennon transaction consists of two \texttt{i\_invoke\_dipatcher} instructions. The first
instruction is always considered as a \emph{free} instruction and resources spent during its execution
session will not be counted. As a result, only the second instruction could fail due to exceeding resource limits.

The Argennon protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs. Every
transaction is required to specify two maximum execution costs: \texttt{maxInternalCost}
and \texttt{maxExternalCost}. The \emph{external} execution cost of a transaction is the \textbf{overall} cost of its
\texttt{invoke\_dispatcher} and \texttt{invoke\_later} instructions,\footnote{By overall cost, we mean the execution
cost needed for reaching the next instruction.} and the remaining execution cost will be considered as
the \emph{internal} cost. If a transaction reaches one of its maximum costs, executing any instruction which has
that type of cost, will throw an AVM exception.

\note{When a transaction reaches its \texttt{maxExternalCost}, it can still keep executing
its own code, while it can not call other smart contracts.
This way the execution cost of a smart contract is completely decoupled from the
smart contract it calls, and a malicious contract can not make its invoker fail unconditionally
by using infinite loops.}

Also, Argennon transactions are required to specify what heap or code area addresses they will access. This will
enable validators to parallelize transaction validation as we will see in Section~\ref{sec:concurrency}. A transaction
that tries to access a memory location that is not in its access list, will be rejected.
Users could use off-chain \emph{smart contract oracles} to predict the list of memory locations their transactions need.

A smart contract oracle is a full AVM emulator that keeps a full local copy of the AVM storage and can emulate AVM
execution without accessing a ZK-EDB server. Smart contract oracles can be used for reporting useful information about
Argennon transactions such as accessed AVM heap or code area locations, exact amount of execution cost,
and so on.

@@

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST bttp://bac.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 69

    {
        "name": "Grant Proposal",
        "recipient": "0x24.0x8f.0x29.0xa1",
        "amount": 25000,
        "sig"= "2a36Gtrw249wQCD70nWY49d"
    }
caps:
    internal: 2500000 # maximum number of AVM execution clocks
    external: 1000000
    read: [(2654,3),(15642,0),(15642,1),(15642,3)]
    write: [(15642,0),(20154,0),(20154,1)]
\end{lstlisting}

@@

A transaction pays
its fees by providing digital signatures of one or more accounts, authorizing the transfer of the amount of fee in
ARG from one or more accounts to the fee sink accounts, and the fee is transferred by the first
\texttt{i\_invoke\_dispatcher} instruction of the transaction.

\note{An Argennon transaction always pays all of its proposed fee, no matter how much of its predefined resources
were not used in the final emulation. This will incentivize users to report the resource usage of their
transactions more accurately.}

>>>>

Argennon has two special smart contracts: the \emph{root smart contract}, also called the \emph{root application}, and
the \emph{ARG smart contract}, which is also called the \emph{Argennon smart contract} or the \emph{ARG application}.

@@

The root application or the root smart contract, with \texttt{applicationID = 0}, is a privileged smart contract
responsible for installation/uninstallation of other smart contracts. The Argennon's root smart contract
performs three main operations:

@@

As a result, every Argennon transaction contains two HTTP requests. Besides these HTTP requests, the
transaction is required to contain a resource declaration object, specifying the maximum amount of resources
it needs for execution.

@@

As we know, every Argennon transaction consists of two \texttt{i\_invoke\_dipatcher} instructions. The first
instruction is always considered as a \emph{free} instruction and resources spent during its execution
session will not be counted. Thus, only the second instruction could fail due to exceeding resource limits.

The Argennon protocol defines an execution cost for
every AVM instruction, reflecting the amount of resources its emulation needs. Every
transaction is required to specify two maximum execution costs: \texttt{maxInternalCost}
and \texttt{maxExternalCost}. The \emph{external} execution cost of a transaction is the \textbf{overall} cost of its
\texttt{invoke\_dispatcher} and \texttt{invoke\_later} instructions,\footnote{By overall cost, we mean the execution
cost needed for reaching the next instruction.}. The remaining execution cost will be considered as
the \emph{internal} cost. If a transaction reaches one of its maximum costs, executing any instruction which has
that type of cost, will throw an AVM exception.

\note{When a transaction reaches its \texttt{maxExternalCost}, it can still keep executing
its own code, while it can not call other smart contracts.
This way the execution cost of a smart contract is completely decoupled from the
smart contract it calls, and a malicious contract can not make its invoker fail
by using infinite loops.}

Also, Argennon transactions are required to specify what heap or code area addresses they will access. This will
enable validators to parallelize transaction validation as we will see in Section~\ref{sec:concurrency}. An instruction
that tries to access a memory location that is not in the access list of the transaction, will throw an exception.
Users could use off-chain \emph{execution oracles} to predict the list of memory locations their transactions need.

An execution oracle is a full AVM emulator that keeps a full local copy of the AVM storage and can emulate AVM
execution without accessing a ZK-EDB server. Execution oracles can be used for reporting useful information about
Argennon transactions such as accessed AVM heap or code area locations, exact amount of execution cost,
and so on.

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST bttp://app.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 77

    {
        "name": "Grant",
        "recipient": "0x24.0x8f.0x29.0xa1",
        "amount": 25000,
        "sig"= "2a36Gtrw249wQCD70nWY49d"
    }
caps:
    internal: 2500000 # maximum number of AVM execution clocks
    external: 1000000
    read: [(2654,3),(15642,0),(15642,1),(15642,3)]
    write: [(15642,0),(20154,0),(20154,1)]
\end{lstlisting}

@@

@@

A transaction pays
its fees by providing digital signatures of one or more accounts, authorizing the transfer of the amount of fee in
ARGs from one or more accounts to the fee sink accounts. This fee is transferred by the first
\texttt{i\_invoke\_dispatcher} instruction of the transaction.

\note{An Argennon transaction always pays all of its proposed fee, no matter how much of its predefined resources
were not used during the final emulation. This will incentivize users to report the resource usage of their
transactions more accurately.}
